Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-29 vertical-thermal-review.Rmd
update figure caption
Thanks, @eoway !

Co-Authored-By: Elsa Ordway <22920153+eoway@users.noreply.github.com>

![**Figure `r fig_model`.** Lidar and thermal remote sensing data can be used to measure vertical canopy structure and plant thermal signatures at increasingly large scales. (a-b) Integrating in situ and remote sensing measurements will support our ability to scale understanding of vertical gradients within and across ecosystems. (c) In turn, these efforts can be used to directly inform ecosystem model development and parameterization. Vertically resolved in situ data could include any variable listed in Table `r table_leaf_traits` or 2.](schematics/fig_remote_sensing.png)

>>>>

![**Figure `r fig_model`.** Lidar and thermal remote sensing data can be used to measure vertical canopy structure and plant thermal signatures at increasingly large scales. (a-b) Integrating in situ and remote sensing measurements will support our ability to scale understanding of vertical gradients within and across ecosystems. (c) In turn, these efforts can be used to directly inform ecosystem model development and parameterization. Vertically resolved in situ data could include any variable listed in Table 1 or 2. Panel b shows drone lidar point cloud data colored with thermal data from a savanna woodland in Kruger National Park, South Africa illustrating vertical and horizontal variation in vegetation temperature. Image courtesy of the Harvard Animal-Landscape Observatory, Peter B. Boucher and Andrew B. Davies.](schematics/fig_remote_sensing.png)
